A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Material

### 2018-11-23 supplementary_materials.tex
Finished run through of SOM

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifespanPriorsParity.pdf}}
	\caption{\textbf{The priors over mean lifespan used to analyse the data for each of the hierarchical models.} The distributional form of the priors is given in Table \ref{tab:dissection_priors}. In all cases the plots show data for 10,000 samples from the relevant prior distribution.}\label{fig:dissection_lifespanPriorsParity}
\end{figure}

@@

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifespanPrior_individual.pdf}}
	\caption{\textbf{The priors over A. mean lifespan and B. over-dispersion parameter used to analyse the individual dissection series.} The prior on the rate parameter of the exponential distribution was $\lambda\sim \text{log-normal}(-1.8,1)$. The prior on the dispersion parameter was $\kappa\sim \text{log-normal}(1,1)$.}\label{fig:dissection_lifespanPrior_individual}
\end{figure}

@@

\newgeometry{scale=0.8}
\thispagestyle{empty}
{%
	\centering
	\includegraphics[page=1,scale=.7]{./Figure_files/dissection_ppcs_all}
	\captionof{figure}{The numbers of mosquitoes recaptured (black lines) versus the 95\% central posterior interval of the posterior predictive distribution (blue shading) for a selection of the dissection series. The titles correspond to the unique combination of "identifier - physiological-experiment-id" in the database. For the rest of the posterior predictive checks for the dissection data models, see the file referenced in the text.}
	\label{fig:dissection_ppc_all1}
	\par
}
\restoregeometry

\newgeometry{scale=0.8}
\thispagestyle{empty}
{%
	\centering
	\includegraphics[page=2,scale=.7]{./Figure_files/dissection_ppcs_all}
	\captionof{figure}{The numbers of mosquitoes recaptured (black lines) versus the 95\% central posterior interval of the posterior predictive distribution (blue shading) for a selection of the dissection series. The titles correspond to the unique combination of "identifier - physiological-experiment-id" in the database. For the rest of the posterior predictive checks for the dissection data models, see the file referenced in the text.}
	\label{fig:dissection_ppc_all2}
	\par
}
\restoregeometry

\newgeometry{scale=0.8}
\thispagestyle{empty}
{%
	\centering
	\includegraphics[page=3,scale=.7]{./Figure_files/dissection_ppcs_all}
	\captionof{figure}{The numbers of mosquitoes recaptured (black lines) versus the 95\% central posterior interval of the posterior predictive distribution (blue shading) for a selection of the dissection series. The titles correspond to the unique combination of "identifier - physiological-experiment-id" in the database. For the rest of the posterior predictive checks for the dissection data models, see the file referenced in the text.}
	\label{fig:dissection_ppc_all3}
	\par
}
\restoregeometry

@@

Since we collected data on the method used to estimate the duration of the gonotrophic cycle we show the raw estimates for the two most common approaches: MRR and laboratory (Fig. \ref{fig:dissection_gonotrophicCycleRaw_MRRVsLab}). From these results it is evident that the estimates from the laboratory studies are, on average, higher than those using the MRR method, (although we wait until Section \ref{sec:dissection_gonotrophicDuration} for a quantitative comparison).

@@

The heterogeneous nature of the gonotrophic cycle estimates requires a method that explicitly accounts for this characteristic of the data. We decided to model the estimates as representing quantiles from an underlying normal distribution that represents uncertainty over possible durations of the gonotrophic cycle. In those circumstances where lower, central and upper bounds were given explicitly the data was fairly symmetric and so we believe assuming the observations come from an unskewed normal distribution is not unreasonable. Explicitly we treated each type of uncertainty interval as follows,

@@

@@

\section{Results}
\subsection{MRR experments}
Figures \ref{fig:mrr_lifeSpanVsRange}, \ref{fig:mrr_lifeSpanVsTrapDensity} and \ref{fig:mrr_temperature} show the estimates of lifespan versus the trapping range, spatial density and temperature at study location. In these cases, the lifespans shown were obtained from the non-hierarchical model with the exponential survival model.

Fig. \ref{fig:mrr_sex} shows the lifespans obtained by sex, for each genus and across all studies ("overall") using the hierarchical Bayesian model with exponential survival model. In the genus-level models, the sex-specific effects (male-only, female-only, mixed-releases) were estimated as independent random effects for each genus with standard normal priors. For the overall model, the sex-specific effects were estimated as independent random effects across all studies, with a standard normal prior.

Fig. \ref{fig:mrr_sugarBlood} shows the lifespans obtained for each pre-release feeding category for each genus and across all studies using the hierarchical Bayesian model with exponential survival model. In the genus-level models, the feeding-specific effects (fed nothing, blood-fed-only, sugar-fed-only and fed both) were estimated as independent random effects for each genus with standard normal priors. For the overall model, the feeding-specific effects were estimated as independent random effects across all studies, with a standard normal prior.

@@

\subsubsection{Table of estimated lifespans estimated from mark-release-recapture studies}

\begin{table}[htbp]
\begin{tabular}{l|l|l|l|l|l|l|l|l}
	\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
 \textit{Aedes} & \textit{simpsoni s.l.} & 6.3 & 11.3 & 18.3 & 31.8 & 75.0 & 26.9 & 29.5 \\
\textit{Aedes} & \textit{communis} & 10.0 & 13.2 & 15.4 & 18.2 & 24.3 & 16.2 & 5.2 \\
\textit{Anopheles} & \textit{koliensis} & 6.7 & 10.5 & 15.2 & 24.0 & 56.5 & 21.9 & 25.2 \\
\textit{Anopheles} & \textit{punctulatus} & 7.2 & 10.7 & 15.1 & 22.8 & 48.9 & 20.3 & 28.6 \\
\textit{Aedes} & \textit{cantans} & 9.7 & 12.0 & 13.9 & 16.1 & 20.6 & 14.4 & 4.7 \\
\textit{Aedes} & \textit{albopictus} & 8.0 & 10.0 & 11.6 & 13.7 & 17.7 & 12.1 & 3.4 \\
\textit{Anopheles} & \textit{albimanus} & 5.9 & 8.6 & 11.6 & 16.9 & 35.7 & 15.2 & 18.7 \\
\textit{Anopheles} & \textit{darlingi} & 4.9 & 7.3 & 10.2 & 16.0 & 37.5 & 14.5 & 14.8 \\
\textit{Anopheles} & \textit{maculatus} & 5.7 & 7.9 & 10.2 & 13.7 & 24.3 & 12.2 & 8.7 \\
\textit{Anopheles} & \textit{culicifacies s.l.} & 4.6 & 7.3 & 9.1 & 11.4 & 18.2 & 10.1 & 6.9 \\
\textit{Anopheles} & \textit{sergenti} & 3.6 & 5.9 & 8.7 & 13.8 & 32.6 & 12.4 & 13.4 \\
\textit{Aedes} & \textit{triseriatus} & 5.6 & 6.6 & 7.5 & 8.5 & 10.7 & 7.7 & 1.8 \\
\textit{Anopheles} & \textit{farauti s.l.} & 4.2 & 5.4 & 6.4 & 7.7 & 10.5 & 6.8 & 2.1 \\
\textit{Aedes} & \textit{africanus} & 3.4 & 5.1 & 6.2 & 7.8 & 11.9 & 7.0 & 9.3 \\
\textit{Aedes} & \textit{aegypti} & 2.8 & 4.5 & 6.2 & 8.5 & 13.9 & 7.0 & 3.8 \\
\textit{Culex} & \textit{quinquefasciatus} & 4.3 & 5.2 & 5.9 & 7.0 & 9.4 & 6.3 & 1.8 \\
\textit{Culex} & \textit{nigripalpus} & 3.5 & 4.6 & 5.8 & 7.5 & 11.3 & 6.4 & 3.1 \\
\textit{Aedes} & \textit{notoscriptus} & 2.9 & 4.0 & 5.4 & 8.2 & 20.2 & 7.9 & 9.5 \\
\textit{Culex} & \textit{pipiens} & 3.4 & 4.4 & 5.2 & 6.4 & 9.0 & 5.6 & 2.0 \\
\textit{Anopheles} & \textit{saperoi} & 3.5 & 4.2 & 4.9 & 5.8 & 8.2 & 5.2 & 2.0 \\
\textit{Anopheles} & \textit{gambiae s.l.} & 3.0 & 3.8 & 4.4 & 5.1 & 6.4 & 4.5 & 1.1 \\
\textit{Aedes} & \textit{melanimon} & 3.3 & 3.9 & 4.3 & 4.8 & 5.7 & 4.4 & 1.0 \\
\textit{Anopheles} & \textit{funestus s.l.} & 2.9 & 3.6 & 4.2 & 4.8 & 6.0 & 4.3 & 1.0 \\
\textit{Anopheles} & \textit{lesteri} & 2.4 & 3.2 & 3.9 & 5.0 & 7.5 & 4.4 & 2.1 \\
\textit{Anopheles} & \textit{quadrimaculatus} & 3.3 & 3.6 & 3.9 & 4.2 & 4.8 & 4.0 & 0.5 \\
\textit{Anopheles} & \textit{pseudopunctipennis s.l.} & 2.3 & 2.9 & 3.5 & 4.3 & 6.7 & 3.8 & 1.9 \\
\textit{Aedes} & \textit{vexans} & 1.9 & 2.3 & 2.6 & 3.0 & 4.1 & 2.8 & 1.0 \\
\textit{Culex} & \textit{tarsalis} & 1.9 & 2.1 & 2.3 & 2.4 & 2.7 & 2.3 & 0.3 \\
\textit{Anopheles} & \textit{vestitipennis} & 1.3 & 1.8 & 2.2 & 2.9 & 4.4 & 2.5 & 1.2 \\
\textit{Anopheles} & \textit{albitarsis s.l.} & 1.3 & 1.6 & 1.9 & 2.2 & 2.9 & 2.0 & 1.0 \\
\textit{Culex} & \textit{tritaeniorhynchus} & 0.7 & 0.9 & 1.1 & 1.2 & 1.6 & 1.1 & 1.0 \\
\textit{Anopheles} & \textit{subpictus s.l.} & 0.4 & 0.6 & 0.8 & 1.1 & 2.4 & 1.1 & 2.6 \\
\hline
\textit{Aedes} & \text{} & 2.8 & 4.8 & 6.9 & 10.0 & 17.2 & 8.1 & 4.9 \\
\textit{Anopheles} & \text{} & 1.5 & 3.0 & 5.0 & 8.4 & 17.8 & 6.8 & 6.4 \\
\textit{Culex} & \text{} & 1.1 & 1.8 & 2.5 & 3.5 & 5.6 & 2.9 & 1.5 \\
\hline
\textbf{Overall} & \text{} & 1.4 & 2.8 & 4.6 & 7.5 & 15.4 & 6.0 & 5.2 \\
\end{tabular}
\caption{Posterior summaries of mean unfed female mosquito lifespan from the MRR analysis. The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
\label{tab:mrr_estimated_lifespans}%
\end{table}%

\subsection{Dissection studies}

\subsubsection{Table of estimated lifespan in terms of gonotrophic cycles and chronological time using dissection data}

\begin{table}[htbp]
\begin{tabular}{l|l|l|l|l|l|l|l|l}
	\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Anopheles} & \textit{sergentii} & 1.0 & 1.9 & 2.5 & 3.4 & 6.2 & 3.0 & 2.5 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 0.7 & 1.2 & 1.9 & 2.9 & 5.4 & 2.4 & 1.9 \\
		\textit{Culex} & \textit{thalassius} & 1.1 & 1.6 & 1.8 & 2.1 & 2.9 & 1.9 & 1.0 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 1.5 & 1.6 & 1.7 & 1.7 & 1.9 & 1.7 & 0.1 \\
		\textit{Anopheles} & \textit{minimus} & 0.7 & 1.2 & 1.7 & 2.2 & 4.1 & 2.0 & 2.2 \\
		\textit{Anopheles} & \textit{maculipennis} & 0.8 & 1.1 & 1.4 & 1.8 & 2.9 & 1.6 & 0.7 \\
		\textit{Culex} & \textit{pipiens} & 1.1 & 1.3 & 1.4 & 1.5 & 1.7 & 1.4 & 0.2 \\
		\textit{Mansonia} & \textit{uniformis} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{rivulorum} & 0.8 & 1.0 & 1.1 & 1.1 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{melas} & 0.8 & 1.0 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{culicifacies} & 0.9 & 1.0 & 1.0 & 1.1 & 1.2 & 1.0 & 0.1 \\
		\textit{Anopheles} & \textit{subpictus} & 0.6 & 0.9 & 1.0 & 1.2 & 2.1 & 1.2 & 2.0 \\
		\textit{Aedes} & \textit{aegypti} & 0.5 & 0.8 & 1.0 & 1.2 & 2.0 & 1.2 & 3.0 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 0.7 & 0.9 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{stephensi} & 0.6 & 0.8 & 1.0 & 1.1 & 1.6 & 1.0 & 0.4 \\
		\textit{Anopheles} & \textit{darlingi} & 0.7 & 0.8 & 0.9 & 1.0 & 1.3 & 1.0 & 0.2 \\
		\textit{Culex} & \textit{quinquefasciatus} & 0.4 & 0.7 & 0.9 & 1.3 & 2.2 & 1.1 & 0.6 \\
		\textit{Aedes} & \textit{polynesiensis} & 0.8 & 0.9 & 0.9 & 0.9 & 1.0 & 0.9 & 0.1 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.3 & 0.6 & 0.9 & 1.3 & 4.2 & 2.5 & 30.8 \\
		\textit{Culex} & \textit{annulirostris} & 0.5 & 0.8 & 0.9 & 1.0 & 1.4 & 0.9 & 0.5 \\
		\textit{Aedes} & \textit{samoanus} & 0.6 & 0.7 & 0.8 & 0.9 & 1.0 & 0.8 & 0.2 \\
		\textit{Aedes} & \textit{sollicitans} & 0.4 & 0.5 & 0.6 & 0.8 & 1.3 & 0.7 & 0.5 \\
		\textit{Aedes} & \textit{vexans} & 0.4 & 0.5 & 0.6 & 0.7 & 0.9 & 0.6 & 0.7 \\
		\textit{Anopheles} & \textit{cruzii} & 0.3 & 0.5 & 0.5 & 0.7 & 1.1 & 0.6 & 0.4 \\
		\textit{Anopheles} & \textit{bellator} & 0.3 & 0.4 & 0.5 & 0.6 & 1.0 & 0.6 & 1.8 \\
		\hline
		\textit{Anopheles} & \textit{} & 0.6 & 1.0 & 1.4 & 1.9 & 3.2 & 1.6 & 0.9 \\
		\textit{Mansonia} & \textit{} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Culex} & \textit{} & 0.5 & 0.8 & 1.0 & 1.4 & 2.3 & 1.2 & 0.6 \\
		\textit{Aedes} & \textit{} & 0.6 & 0.7 & 0.8 & 0.9 & 1.1 & 0.8 & 0.2 \\
		\hline
		\textbf{Overall} & \textit{} & 0.5 & 0.8 & 1.2 & 1.7 & 2.7 & 1.3 & 0.7 \\
	\end{tabular}
\caption{Posterior summaries of mean mosquito lifespan in terms of gonotrophic cycles from dissection studies. The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
\label{tab:dissection_estimated_lifespans}%
\end{table}

\subsubsection{Chronological lifespan estimates}
\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifetimes_exponential_chron.pdf}}
	\caption{\textbf{Posterior estimates of female mosquito mean chronological lifespan across species, genus and overall groupings as determined from the dissection data.} The lifespans shown are for mosquitoes that were not fed with sugar or blood (for females) before release. The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:dissection_lifetimes_exponential_chron}
\end{figure}

>>>>

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifespanPriorsParity.pdf}}
	\caption{\textbf{The priors for mean lifespan used to analyse the data for each of the hierarchical models.} The distributional form of the priors is given in Table \ref{tab:dissection_priors}. In all cases the plots show data for 10,000 samples from the relevant prior distribution.}\label{fig:dissection_lifespanPriorsParity}
\end{figure}

@@

\begin{figure}[ht]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifespanPrior_individual.pdf}}
	\caption{\textbf{The priors for A. mean lifespan and B. the over-dispersion parameter used to analyse the individual dissection series.} The prior on the rate parameter of the exponential distribution was $\lambda\sim \text{log-normal}(-1.8,1)$. The prior on the dispersion parameter was $\kappa\sim \text{log-normal}(1,1)$.}\label{fig:dissection_lifespanPrior_individual}
\end{figure}

@@

\newgeometry{scale=0.8}
\thispagestyle{empty}
{%
	\centering
	\includegraphics[page=1,scale=.7]{./Figure_files/dissection_ppcs_all}
	\captionof{figure}{\textbf{The numbers of mosquitoes recaptured (black lines) versus the 95\% central posterior interval of the posterior predictive distribution (blue shading) for a selection of the dissection series.} The titles correspond to the unique combination of "identifier - physiological-experiment-id" in the database. For the rest of the posterior predictive checks for the dissection data models, see the file referenced in the text.}
	\label{fig:dissection_ppc_all1}
	\par
}
\restoregeometry

\newgeometry{scale=0.8}
\thispagestyle{empty}
{%
	\centering
	\includegraphics[page=2,scale=.7]{./Figure_files/dissection_ppcs_all}
	\captionof{figure}{\textbf{The numbers of mosquitoes recaptured (black lines) versus the 95\% central posterior interval of the posterior predictive distribution (blue shading) for a selection of the dissection series.} The titles correspond to the unique combination of "identifier - physiological-experiment-id" in the database. For the rest of the posterior predictive checks for the dissection data models, see the file referenced in the text.}
	\label{fig:dissection_ppc_all2}
	\par
}
\restoregeometry

\newgeometry{scale=0.8}
\thispagestyle{empty}
{%
	\centering
	\includegraphics[page=3,scale=.7]{./Figure_files/dissection_ppcs_all}
	\captionof{figure}{\textbf{The numbers of mosquitoes recaptured (black lines) versus the 95\% central posterior interval of the posterior predictive distribution (blue shading) for a selection of the dissection series.} The titles correspond to the unique combination of "identifier - physiological-experiment-id" in the database. For the rest of the posterior predictive checks for the dissection data models, see the file referenced in the text.}
	\label{fig:dissection_ppc_all3}
	\par
}
\restoregeometry

@@

Since we collected data on the method used to estimate the duration of the gonotrophic cycle we show the raw estimates for the two most common approaches: MRR and laboratory (Fig. \ref{fig:dissection_gonotrophicCycleRaw_MRRVsLab}). From these results it is evident that the estimates from the laboratory studies are, on average, higher than those using the MRR method.

@@

The heterogeneous nature of the gonotrophic cycle estimates requires a method that explicitly accounts for this characteristic of the data. We decided to model the estimates as representing quantiles from an underlying normal distribution that represents uncertainty over possible durations of the gonotrophic cycle. In those circumstances where lower, central and upper bounds were given explicitly the data was fairly symmetric and so we believe assuming the observations come from an unskewed normal distribution is reasonable. Explicitly we treated each type of uncertainty interval as follows,

@@

Using the collected data, we estimated that uncertainty in the first gonotrophic cycle duration is estimated as $\mathcal{N}(4.26, 0.38)$ and, for subsequent cycles, $\mathcal{N}(3.85, 0.35)$.

@@

\section{Results}
\subsection{MRR experments}
Figures \ref{fig:mrr_lifeSpanVsRange} and \ref{fig:mrr_lifeSpanVsTrapDensity} show the estimates of lifespan versus the trapping range and spatial density of traps at study location. In these cases, the lifespans shown were obtained from the non-hierarchical model with the exponential survival model. The spatial density of traps was obtained assuming that the study area was a circular area of radius equal to the maximum trapping distance.

Fig. \ref{fig:mrr_female_blood_sugar} shows the lifespans obtained for each pre-release feeding category for each genus and across all studies using the hierarchical Bayesian model with exponential survival model. In the genus-level models, the feeding-specific effects (not pre-fed, blood-fed-only and sugar-fed-only) were estimated as independent random effects for each genus with standard normal priors. For the overall model, the feeding-specific effects were estimated as independent random effects across all studies, with a standard normal prior.

@@

\begin{table}[htbp]
\begin{tabular}{l|l|l|l|l|l|l|l|l}
	\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
 \textit{Aedes} & \textit{simpsoni s.l.} & 6.3 & 11.3 & 18.3 & 31.8 & 75.0 & 26.9 & 29.5 \\
\textit{Aedes} & \textit{communis} & 10.0 & 13.2 & 15.4 & 18.2 & 24.3 & 16.2 & 5.2 \\
\textit{Anopheles} & \textit{koliensis} & 6.7 & 10.5 & 15.2 & 24.0 & 56.5 & 21.9 & 25.2 \\
\textit{Anopheles} & \textit{punctulatus} & 7.2 & 10.7 & 15.1 & 22.8 & 48.9 & 20.3 & 28.6 \\
\textit{Aedes} & \textit{cantans} & 9.7 & 12.0 & 13.9 & 16.1 & 20.6 & 14.4 & 4.7 \\
\textit{Aedes} & \textit{albopictus} & 8.0 & 10.0 & 11.6 & 13.7 & 17.7 & 12.1 & 3.4 \\
\textit{Anopheles} & \textit{albimanus} & 5.9 & 8.6 & 11.6 & 16.9 & 35.7 & 15.2 & 18.7 \\
\textit{Anopheles} & \textit{darlingi} & 4.9 & 7.3 & 10.2 & 16.0 & 37.5 & 14.5 & 14.8 \\
\textit{Anopheles} & \textit{maculatus} & 5.7 & 7.9 & 10.2 & 13.7 & 24.3 & 12.2 & 8.7 \\
\textit{Anopheles} & \textit{culicifacies s.l.} & 4.6 & 7.3 & 9.1 & 11.4 & 18.2 & 10.1 & 6.9 \\
\textit{Anopheles} & \textit{sergenti} & 3.6 & 5.9 & 8.7 & 13.8 & 32.6 & 12.4 & 13.4 \\
\textit{Aedes} & \textit{triseriatus} & 5.6 & 6.6 & 7.5 & 8.5 & 10.7 & 7.7 & 1.8 \\
\textit{Anopheles} & \textit{farauti s.l.} & 4.2 & 5.4 & 6.4 & 7.7 & 10.5 & 6.8 & 2.1 \\
\textit{Aedes} & \textit{africanus} & 3.4 & 5.1 & 6.2 & 7.8 & 11.9 & 7.0 & 9.3 \\
\textit{Aedes} & \textit{aegypti} & 2.8 & 4.5 & 6.2 & 8.5 & 13.9 & 7.0 & 3.8 \\
\textit{Culex} & \textit{quinquefasciatus} & 4.3 & 5.2 & 5.9 & 7.0 & 9.4 & 6.3 & 1.8 \\
\textit{Culex} & \textit{nigripalpus} & 3.5 & 4.6 & 5.8 & 7.5 & 11.3 & 6.4 & 3.1 \\
\textit{Aedes} & \textit{notoscriptus} & 2.9 & 4.0 & 5.4 & 8.2 & 20.2 & 7.9 & 9.5 \\
\textit{Culex} & \textit{pipiens} & 3.4 & 4.4 & 5.2 & 6.4 & 9.0 & 5.6 & 2.0 \\
\textit{Anopheles} & \textit{saperoi} & 3.5 & 4.2 & 4.9 & 5.8 & 8.2 & 5.2 & 2.0 \\
\textit{Anopheles} & \textit{gambiae s.l.} & 3.0 & 3.8 & 4.4 & 5.1 & 6.4 & 4.5 & 1.1 \\
\textit{Aedes} & \textit{melanimon} & 3.3 & 3.9 & 4.3 & 4.8 & 5.7 & 4.4 & 1.0 \\
\textit{Anopheles} & \textit{funestus s.l.} & 2.9 & 3.6 & 4.2 & 4.8 & 6.0 & 4.3 & 1.0 \\
\textit{Anopheles} & \textit{lesteri} & 2.4 & 3.2 & 3.9 & 5.0 & 7.5 & 4.4 & 2.1 \\
\textit{Anopheles} & \textit{quadrimaculatus} & 3.3 & 3.6 & 3.9 & 4.2 & 4.8 & 4.0 & 0.5 \\
\textit{Anopheles} & \textit{pseudopunctipennis s.l.} & 2.3 & 2.9 & 3.5 & 4.3 & 6.7 & 3.8 & 1.9 \\
\textit{Aedes} & \textit{vexans} & 1.9 & 2.3 & 2.6 & 3.0 & 4.1 & 2.8 & 1.0 \\
\textit{Culex} & \textit{tarsalis} & 1.9 & 2.1 & 2.3 & 2.4 & 2.7 & 2.3 & 0.3 \\
\textit{Anopheles} & \textit{vestitipennis} & 1.3 & 1.8 & 2.2 & 2.9 & 4.4 & 2.5 & 1.2 \\
\textit{Anopheles} & \textit{albitarsis s.l.} & 1.3 & 1.6 & 1.9 & 2.2 & 2.9 & 2.0 & 1.0 \\
\textit{Culex} & \textit{tritaeniorhynchus} & 0.7 & 0.9 & 1.1 & 1.2 & 1.6 & 1.1 & 1.0 \\
\textit{Anopheles} & \textit{subpictus s.l.} & 0.4 & 0.6 & 0.8 & 1.1 & 2.4 & 1.1 & 2.6 \\
\hline
\textit{Aedes} & \text{} & 2.8 & 4.8 & 6.9 & 10.0 & 17.2 & 8.1 & 4.9 \\
\textit{Anopheles} & \text{} & 1.5 & 3.0 & 5.0 & 8.4 & 17.8 & 6.8 & 6.4 \\
\textit{Culex} & \text{} & 1.1 & 1.8 & 2.5 & 3.5 & 5.6 & 2.9 & 1.5 \\
\hline
\textbf{Overall} & \text{} & 1.4 & 2.8 & 4.6 & 7.5 & 15.4 & 6.0 & 5.2 \\
\end{tabular}
\caption{\textbf{Posterior summaries of mean unfed female mosquito lifespan from the MRR analysis.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
\label{tab:mrr_estimated_lifespans}%
\end{table}%

\subsection{Dissection studies}
Tables \ref{tab:dissection_estimated_lifespans} and \ref{tab:dissection_estimated_lifespans_chron} show posterior summaries of lifespan estimated from the dissection analysis, in terms of gonotrophic cycles and chronological time, respectively.

\begin{table}[htbp]
\begin{tabular}{l|l|l|l|l|l|l|l|l}
	\textbf{Genus} & \textbf{Species} & \textbf{5$\%$} & \textbf{25$\%$} & \textbf{50$\%$} & \textbf{75$\%$} & \textbf{95\%} &  \textbf{Mean} & \textbf{Std. dev.}\\
		\hline
		\textit{Anopheles} & \textit{sergentii} & 1.0 & 1.9 & 2.5 & 3.4 & 6.2 & 3.0 & 2.5 \\
		\textit{Anopheles} & \textit{gambiae s.l.} & 0.7 & 1.2 & 1.9 & 2.9 & 5.4 & 2.4 & 1.9 \\
		\textit{Culex} & \textit{thalassius} & 1.1 & 1.6 & 1.8 & 2.1 & 2.9 & 1.9 & 1.0 \\
		\textit{Anopheles} & \textit{farauti s.l.} & 1.5 & 1.6 & 1.7 & 1.7 & 1.9 & 1.7 & 0.1 \\
		\textit{Anopheles} & \textit{minimus} & 0.7 & 1.2 & 1.7 & 2.2 & 4.1 & 2.0 & 2.2 \\
		\textit{Anopheles} & \textit{maculipennis} & 0.8 & 1.1 & 1.4 & 1.8 & 2.9 & 1.6 & 0.7 \\
		\textit{Culex} & \textit{pipiens} & 1.1 & 1.3 & 1.4 & 1.5 & 1.7 & 1.4 & 0.2 \\
		\textit{Mansonia} & \textit{uniformis} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{rivulorum} & 0.8 & 1.0 & 1.1 & 1.1 & 1.4 & 1.1 & 0.2 \\
		\textit{Anopheles} & \textit{melas} & 0.8 & 1.0 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{culicifacies} & 0.9 & 1.0 & 1.0 & 1.1 & 1.2 & 1.0 & 0.1 \\
		\textit{Anopheles} & \textit{subpictus} & 0.6 & 0.9 & 1.0 & 1.2 & 2.1 & 1.2 & 2.0 \\
		\textit{Aedes} & \textit{aegypti} & 0.5 & 0.8 & 1.0 & 1.2 & 2.0 & 1.2 & 3.0 \\
		\textit{Anopheles} & \textit{quadrimaculatus} & 0.7 & 0.9 & 1.0 & 1.1 & 1.3 & 1.0 & 0.2 \\
		\textit{Anopheles} & \textit{stephensi} & 0.6 & 0.8 & 1.0 & 1.1 & 1.6 & 1.0 & 0.4 \\
		\textit{Anopheles} & \textit{darlingi} & 0.7 & 0.8 & 0.9 & 1.0 & 1.3 & 1.0 & 0.2 \\
		\textit{Culex} & \textit{quinquefasciatus} & 0.4 & 0.7 & 0.9 & 1.3 & 2.2 & 1.1 & 0.6 \\
		\textit{Aedes} & \textit{polynesiensis} & 0.8 & 0.9 & 0.9 & 0.9 & 1.0 & 0.9 & 0.1 \\
		\textit{Culex} & \textit{tritaeniorhynchus} & 0.3 & 0.6 & 0.9 & 1.3 & 4.2 & 2.5 & 30.8 \\
		\textit{Culex} & \textit{annulirostris} & 0.5 & 0.8 & 0.9 & 1.0 & 1.4 & 0.9 & 0.5 \\
		\textit{Aedes} & \textit{samoanus} & 0.6 & 0.7 & 0.8 & 0.9 & 1.0 & 0.8 & 0.2 \\
		\textit{Aedes} & \textit{sollicitans} & 0.4 & 0.5 & 0.6 & 0.8 & 1.3 & 0.7 & 0.5 \\
		\textit{Aedes} & \textit{vexans} & 0.4 & 0.5 & 0.6 & 0.7 & 0.9 & 0.6 & 0.7 \\
		\textit{Anopheles} & \textit{cruzii} & 0.3 & 0.5 & 0.5 & 0.7 & 1.1 & 0.6 & 0.4 \\
		\textit{Anopheles} & \textit{bellator} & 0.3 & 0.4 & 0.5 & 0.6 & 1.0 & 0.6 & 1.8 \\
		\hline
		\textit{Anopheles} & \textit{} & 0.6 & 1.0 & 1.4 & 1.9 & 3.2 & 1.6 & 0.9 \\
		\textit{Mansonia} & \textit{} & 0.9 & 1.1 & 1.1 & 1.2 & 1.4 & 1.1 & 0.2 \\
		\textit{Culex} & \textit{} & 0.5 & 0.8 & 1.0 & 1.4 & 2.3 & 1.2 & 0.6 \\
		\textit{Aedes} & \textit{} & 0.6 & 0.7 & 0.8 & 0.9 & 1.1 & 0.8 & 0.2 \\
		\hline
		\textbf{Overall} & \textit{} & 0.5 & 0.8 & 1.2 & 1.7 & 2.7 & 1.3 & 0.7 \\
	\end{tabular}
\caption{\textbf{Posterior summaries of mean female mosquito lifespan in terms of gonotrophic cycles from dissection studies.} The 5\%, 25\%, 50\%, 75\% and 95\% columns indicate the respective quantiles of the posterior distribution for mean lifespan, and the `Mean' and `Std. dev.' columns indicate the posterior mean and standard deviation of mean lifespan.}
\label{tab:dissection_estimated_lifespans}%
\end{table}

\begin{figure}[h]
	\centerline{\includegraphics[width=1\textwidth]{./Figure_files/dissection_lifetimes_exponential_chron.pdf}}
	\caption{\textbf{Posterior estimates of female mosquito mean chronological lifespan across species, genus and overall groupings as determined from the dissection data.} The lifespans shown are for mosquitoes that were not fed with sugar or blood (for females) before release. The middle line in each box shows the median estimates and the solid dot indicates the mean. The left and right box edges show the 25\%, and 75\% posterior quantiles respectively. The whiskers show the range of the data, excluding points lying more than 1.5 times the interquartile range away from each edge of the box. The numbers before the start of the left whisker indicate the number of individual time-series within each species. All estimates were obtained using the hierarchical exponential survival model.}
	\label{fig:dissection_lifetimes_exponential_chron}
\end{figure}
